---
title: "Coronavirus (COVID-19) Cases Summary"
output: ioslides_presentation
author: Shaopeng Li
date: 08/03/2020
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## COVID-19 pandemic

The COVID‑19 pandemic, also known as the coronavirus pandemic, is an ongoing global pandemic of coronavirus disease 2019 (COVID‑19), caused by severe acute respiratory syndrome coronavirus 2 (SARS‑CoV‑2). The outbreak was first identified in December 2019 in Wuhan, China.The World Health Organization declared the outbreak a Public Health Emergency of International Concern on 30 January 2020 and a pandemic on 11 March.

**From Wikipedia, the free encyclopedia**

## Symptoms

People with COVID-19 have had a wide range of symptoms reported – ranging from mild symptoms to severe illness. Symptoms may appear 2-14 days after exposure to the virus. People with these symptoms may have COVID-19:

- Fever or chills
- Cough
- Shortness of breath or difficulty breathing
- Fatigue
- Muscle or body aches
- Headache

## Global Reported Cases
```{r,echo=FALSE,message=FALSE}
library(dplyr)
library(plotly)
require(devtools)
covid19toatl <- read.csv("C:/Users/shaopeng.li/Downloads/owid_covid_data.csv",na.strings = "")
covid19us <- filter(covid19toatl,continent=="North America",location=="United States")%>%
  arrange(date)
covid19toatl<-covid19toatl[!is.na(covid19toatl$continent),]%>%group_by(continent,date)%>%summarise(sum(total_cases))%>%mutate(totalcase=`sum(total_cases)`)
plot_ly(as.data.frame(covid19toatl), x = ~date, y = ~totalcase, color = ~continent) %>%
  add_trace(colors = "Set1", type = "scatter", mode = "lines",connectgaps=TRUE) %>%
  layout(xaxis = list(title = "Date"), yaxis = list(title = "Total Cases"))
```

## U.S. Reported Cases
```{r cars, echo=FALSE,message=FALSE}
plot_ly(data=covid19us, x = ~date, y = ~total_cases)%>%
  layout(xaxis = list(title = "Date"), yaxis = list(title = "Total Cases"))
```

## Prevent Getting Sick

- Cleaning and Disinfecting Your Home
- Social Distancing
- Masks
- Wearing Gloves
